Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[scale=2.3]{figures/sample_sequence.eps}
    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
    \label{fig:sample_sequence}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{}
    \caption{The baseline UBEM for Wesbrook Village in BC.}
    \label{fig:wesbrook_base}
\end{figure}

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.0]{figures/general_results.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

@@

@@

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=1]{figures/true_macc_noDH_waterfall.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH_waterfall}
% \end{figure}

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_noDH.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH}
% \end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_noDH}
\end{figure}

@@

% \begin{figure*}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_dh.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH}
% \end{figure*}

% \begin{figure}[hbpt]
%     \centering
%     \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH_waterfall}
% \end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH}
\end{figure}

@@

%---------------------------------------------------------------------------------------
This document is a summary of various documents from previous Building Simulation Conferences.
%here starts the references
\bibliographystyle{BS2021}
\bibliography{bs2021_ref}
% \newpage
% \onecolumn
% Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.
\end{document}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[scale=1.5]{figures/sample_sequence.eps}
%     \caption{Each scenario iterated through 256 combinations of strategy implementation.}
%     \label{fig:sample_sequence}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics{}
%     \caption{The baseline UBEM for Wesbrook Village in BC.}
%     \label{fig:wesbrook_base}
% \end{figure}

@@

\begin{figure}[hbt]
    \centering
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/true_maccs_waterfalls_both.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:true_macc_both}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_noDH_waterfall_comb.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_noDH}
% \end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[scale=0.8]{figures/true_macc_DH_waterfall_comb.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:MACC_true_DH}
% \end{figure}

@@

%---------------------------------------------------------------------------------------
\footnotesize
\bibliographystyle{BS2021}
\bibliography{bs2021_ref}
% \newpage
% \onecolumn
% Please \textbf{do not} include this disclaimer in your paper.  You will be required to accept these conditions when you  submit your paper via the web site.
\end{document}
